---
title: "Carbon"
author: "Vincent Bisquay Gracia"
date: "12/05/2021"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

# I. set up

Used pakages :

```{r setup, message=FALSE, warning=FALSE}

wd = "D:/Internship 3A/GitHub/Project-Klamath-2021/Outputs/R"

setwd(wd)
library(magrittr)
library(cowplot)
library(ggplot2)
library(raster)
#library(rasterVis)
library(knitr)
library(tibble)
library(dplyr)

```

```{r data}

BAU_input =
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest BAU/"
Adapty_input = 
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest Adaptability/"
ProAct_input =
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest Pro-active/"

BAU_inputBM1 = 
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest BAU/..1/biomass/"
Adapty_inputBM1 = 
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest Adaptability/..1/biomass/"
ProAct_inputBM1 =
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest Pro-active/..1/biomass/"

BAU_inputBM2 = 
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest BAU/..2/biomass/"
Adapty_inputBM2 = 
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest Adaptability/..2/biomass/"
ProAct_inputBM2 =
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest Pro-active/..2/biomass/"

ListScenario = c("BAU","Adapty")#,"ProAct")

```



```{r col}
pal.2 = colorRampPalette(c("purple","yellow"))

pal.dif = colorRampPalette(c("red","tomato", "darkgoldenrod1","cyan3","cyan","blue"))

```


# II. Carbon balance

# III. Resilience and disturbancies regimes

The biomass killed by fires coming from lightnings (natural fire mortality), by fires coming from human activity (called here accidental fires, even if they can be intentionnal) and by insects (insect mortality) is compared on the different scenarios. To avoid an overestimation of mortality and to make sure that all the data frames havethe same length, the years without insect outbreak are added with a mortality of 0.

## III.a) Mortality due to disturbancies


```{r mort}

Mortality = data.frame()

for(j in c(1,2)){
  
  if(j == 1) { run = "..1"
  } else { run = "..2"}

  for(scenario in ListScenario){
    
    if(scenario == "BAU") {Input = BAU_input
    } else if(scenario == "Adapty"){Input = Adapty_input
    } else {Input = ProAct_input}

    BDA_Tot = paste(Input, run, "/bda_log.csv",sep="") %>% read.csv()
    BDA = cbind(BDA_Tot$Time, BDA_Tot$TotalBiomassMortality) %>% as.data.frame()
    colnames(BDA) = c("Time", "Mortality")

    BDA = aggregate(BDA$Mortality, by=list(Time=BDA$Time), FUN=sum)

    colnames(BDA) = c("Time", "Mortality")


    for(i in (1:100)){
      if(!(i %in% BDA$Time)){
      BDA = rbind(BDA, c(i,0))
      }
    }

    BDA$Disturbancy = "Insects"
    BDA$Scenario = scenario
    BDA$Run = j

    scrapple_Tot = paste(Input, run, "/scrapple-summary-log.csv", sep="") %>% read.csv()
    scrapple_Acc = cbind(scrapple_Tot$SimulationYear,
                    scrapple_Tot$TotalBiomassMortalityAccidental) %>% as.data.frame()
    colnames(scrapple_Acc) = c("Time", "Mortality")
    scrapple_Acc$Disturbancy = "Fire accidental"
    scrapple_Acc$Scenario = scenario
    scrapple_Acc$Run = j

    scrapple_Nat = cbind(scrapple_Tot$SimulationYear,
                    scrapple_Tot$TotalBiomassMortalityLightning) %>% as.data.frame()
    colnames(scrapple_Nat) = c("Time", "Mortality")
    scrapple_Nat$Disturbancy = "Fire lightning"
    scrapple_Nat$Scenario = scenario
    scrapple_Nat$Run = j
  
    Harvest_Tot =  paste(Input, run, "/harvest/summary-log.csv",sep="") %>% read.csv()
    Harvest = Harvest_Tot %>% group_by(Time) %>%
      summarise(TotalBiomassHarvested = sum(TotalBiomassHarvested))
    colnames(Harvest) = c("Time", "Mortality")
    Harvest$Mortality = Harvest$Mortality %>% as.numeric()
    Harvest$Mortality = Harvest$Mortality*100 # convertion Mg/ha in g/m²
    Harvest$Disturbancy = "Harvest"
    Harvest$Scenario = scenario
    Harvest$Run = j
  
    Mortality = rbind(Mortality, BDA, scrapple_Acc, scrapple_Nat, Harvest)
  }
}
  
```

The biomass removed by harvest is also added as a mortality.

```{r regroup}

Mortality_Agg = Mortality %>% group_by(Disturbancy, Scenario) %>%
      summarise(MortalityMean = mean(Mortality), MortalitySd = sd(Mortality))

Mortality_AggT = Mortality %>% group_by(Time, Disturbancy, Scenario) %>%
      summarise(MortalityMean = mean(Mortality), MortalitySd = sd(Mortality))

```



```{r mort2, message=F, warning=F}


ggplot(Mortality_AggT, aes(x=Time, y=MortalityMean, col=Disturbancy, group=Disturbancy)) +
  geom_line()+
  geom_errorbar(aes(ymin=MortalityMean-MortalitySd, ymax=MortalityMean+MortalitySd)) +
  xlab("Time (years)") +
  ylab("Mortality in biomass") +
  ggtitle("Evolution of mortality due to disturbancies on different scenarios") +
  theme(plot.title = element_text(hjust = 0.5))+
  facet_wrap(~Scenario, ncol=1)

```

```{r}

ggplot(Mortality_Agg, aes(x=Disturbancy, y=MortalityMean, fill = Disturbancy)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin=MortalityMean-MortalitySd, ymax=MortalityMean+MortalitySd)) +
  xlab("Type of disturbancy") +
  ylab("Mortality in biomass") +
  ggtitle("Total mortality by scenario") +
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~Scenario, ncol=3)

```

## verify no adjusting



Non parametric test and paired => Wilcoxon Test

```{r comp}
TestData = data.frame()

for (disturbance in c("Insects","Fire accidental", "Fire lightning", "Harvest")) {
  for (scenario in ListScenario) {
    Mort = Mortality$Mortality[Mortality$Disturbancy==disturbance &
                                 Mortality$Scenario==scenario] %>%
                                  as.numeric() %>% as.data.frame()
    names(Mort) = paste0(disturbance,"_",scenario)
    if (nrow(TestData) == 0) {
      TestData = Mort
    } else {
      TestData = cbind(TestData, Mort)
    }
  }
  
  
}

j=(1:8)
TestData[ , j] = apply(TestData[ , j], 2,
                    function(x) as.numeric(as.character(x)))

kable(as.data.frame(Mortality_Agg), caption = "Mortality depending on the scenario")

```


### III.a.1) Harvest

```{r harvestplot}

ggplot(Mortality_Agg[Mortality_Agg$Disturbancy=="Harvest",], aes(x=Scenario, y=MortalityMean, fill=Scenario)) +
geom_bar(stat="identity") +
geom_errorbar(aes(ymin=MortalityMean-MortalitySd, ymax=MortalityMean+MortalitySd)) +
ylab("Biomass removed") +
ggtitle("Harvest by scenario") +
theme(plot.title = element_text(hjust = 0.5))

```

```{r harvestest}

shapiro.test(TestData$Harvest_BAU)
shapiro.test(TestData$Harvest_Adapty)
#shapiro.test(TestData$Harvest_ProAct)

wilcox.test(TestData$Harvest_BAU, TestData$Harvest_Adapty)
wilcox.test(TestData$Harvest_BAU, TestData$Harvest_ProAct)
#wilcox.test(TestData$Harvest_Adapty, TestData$Harvest_ProAct)

```


### III.b.2) Insects

```{r InsectComp}

ggplot(Mortality_Agg[Mortality_Agg$Disturbancy=="Insects",], aes(x=Scenario, y=MortalityMean, fill=Scenario)) +
geom_bar(stat="identity") +
geom_errorbar(aes(ymin=MortalityMean-MortalitySd, ymax=MortalityMean+MortalitySd)) +
ylab("Biomass killed") +
ggtitle("Insect outbreak by scenario") +
theme(plot.title = element_text(hjust = 0.5))

#kable(as.data.frame(cbind(MorTable$Scenario[MorTable$Disturbancy=="Insects"],
#                          MorTable$Table[MorTable$Disturbancy=="Insects"])))

```

```{r insectstest}

shapiro.test(TestData$Insects_BAU)
shapiro.test(TestData$Insects_Adapty)
#shapiro.test(TestData$Harvest_ProAct)

wilcox.test(TestData$Harvest_BAU, TestData$Insects_Adapty)
wilcox.test(TestData$Harvest_BAU, TestData$Insects_ProAct)
#wilcox.test(TestData$Harvest_Adapty, TestData$Harvest_ProAct)

```

p-hacking


### III.c.3) Fire

  i) Accidental

Don't consider the Rx here

```{r FireAcplot, message=F, warning=F}

ggplot(Mortality_Agg[Mortality_Agg$Disturbancy=="Fire accidental",], aes(x=Scenario, y=MortalityMean, fill=Scenario)) +
geom_bar(stat="identity") +
geom_errorbar(aes(ymin=MortalityMean-MortalitySd, ymax=MortalityMean+MortalitySd)) +
ylab("Biomass burned") +
ggtitle("Biomass burned accidentaly by scenario") +
theme(plot.title = element_text(hjust = 0.5))

```

  ii) Natural

```{r FireNat}
ggplot(Mortality[Mortality$Disturbancy=="Fire lightning",], aes(x=Scenario, y=Mortality, fill=Scenario)) +
geom_bar(stat="identity") +
ylab("Biomass burned") +
ggtitle("Biomass burned naturaly by scenario") +
theme(plot.title = element_text(hjust = 0.5))

```

```{r fireacctest}

shapiro.test(TestData$Fire lightning_BAU)
shapiro.test(TestData$Fire lightning_Adapty)
#shapiro.test(TestData$Harvest_ProAct)

wilcox.test(TestData$Harvest_BAU, TestData$Fire lightning_Adapty)
wilcox.test(TestData$Harvest_BAU, TestData$Fire lightning_ProAct)
#wilcox.test(TestData$Harvest_Adapty, TestData$Harvest_ProAct)

```

Mean mortality, max, f pics

biomass recover after disturbancy (slope).

```{r fire}
Zero = paste0(BAU_input, "..1/scrapple-fire/flaming-consumptions-1.img") %>% raster()

Zero[Zero != 0] = 0

RasterStack_Burn = stack()
RasterStack_AllF = stack()
RasterStack_AccF = stack()
RasterStack_NatF = stack()
RasterStack_RxF = stack()

for(scenario in ListScenario){
    
  if(scenario == "BAU") {
    Input = BAU_input
    TotBurn = Zero
    FreqAllT = Zero
    FreqAcc = Zero
    FreqNat = Zero
    FreqRx = Zero
  } else if(scenario == "Adapty"){
    Input = Adapty_input
    TotBurn = Zero
    TotBurn = Zero
    FreqAllT = Zero
    FreqAcc = Zero
    FreqNat = Zero
    FreqRx = Zero
  } else {
    Input = ProAct_input
    TotBurn = Zero
    TotBurn = Zero
    FreqAllT = Zero
    FreqAcc = Zero
    FreqNat = Zero
    FreqRx = Zero}
  
  for (i in 1:100) {
    Raster_fc = paste0(Input, "..1/scrapple-fire/flaming-consumptions-",i,".img") %>% raster()
    Raster_sm = paste0(Input, "..1/scrapple-fire/smolder-consumption-",i,".img") %>% raster()
    RasterBurn = Raster_fc + Raster_sm
    TotBurn = TotBurn + RasterBurn
    
    Raster_FT = paste0(Input, "..1/scrapple-fire/ignition-type-",i,".img") %>% raster()
    
    Raster_FT[Raster_FT == 1] = 0
    
    Raster_AllT = Raster_FT
    Raster_FT[Raster_FT != 0] = 1
    FreqAllT = FreqAllT + Raster_FT
    
    Raster_Acc = Raster_FT
    Raster_Acc[Raster_Acc != 2] = 0
    Raster_Acc[Raster_Acc == 2] = 1
    FreqAcc = FreqAcc + Raster_Acc
    
    Raster_Nat = Raster_FT
    Raster_Nat[Raster_Nat != 3] = 0
    Raster_Nat[Raster_Nat == 3] = 1
    FreqNat = FreqNat + Raster_Nat   
    
    Raster_Rx = Raster_FT
    Raster_Rx[Raster_Rx != 4] = 0
    Raster_Rx[Raster_Rx == 4] = 1
    FreqRx = FreqRx + Raster_Rx

    if(i==100){
      #TotBurn[TotBurn == 0] = NA
      names(TotBurn) = scenario
      RasterStack_Burn = stack(RasterStack_Burn, TotBurn)
      
      #FreqAllT[FreqAllT == 0] = NA
      names(FreqAllT) = paste0(scenario,"all")
      RasterStack_AllF = stack(RasterStack_AllF, FreqAllT)
      
      #FreqAcc[FreqAcc == 0] = NA
      names(FreqAcc) = paste0(scenario,"Acc")
      RasterStack_AccF = stack(RasterStack_AccF, FreqAcc)
      
      #FreqNat[FreqNat == 0] = NA
      names(Raster_Nat) = paste0(scenario,"Nat")
      RasterStack_NatF = stack(RasterStack_NatF, FreqNat)
      
      #FreqRx[FreqRx == 0] = NA
      names(FreqRx) = paste0(scenario,"Rx")
      RasterStack_RxF = stack(RasterStack_RxF, FreqRx)
      
    }
      }
}

```

```{r Burn}

VarSatck = RasterStack_Burn
  Max = max(maxValue(VarSatck))+1
  Min = min(minValue(VarSatck))
  brks = seq(Min,Max,by=0.1)
  nbrks = length(brks)-1
  r.range = c(Min, Max)
  
rasTot = raster(ncol=2, nrow=1)
values(rasTot) = c(Min,Max)

par(mfrow=c(1,3))

plot(VarSatck, breaks=brks,col=pal.2(nbrks), legend = F, zlim=c(Min,Max), 
main = "Sum of biomass burned")
plot(rasTot, legend.only=TRUE, col=pal.2(nbrks),
    legend.width=1, legend.shrink=0.75,
    legend.args=list(text="??",
                     side=4, font=2, line=2.5, cex=0.8))

```


```{r tipe}

VarSatck = stack(RasterStack_AllF, RasterStack_AccF, RasterStack_NatF,RasterStack_RxF)
  Max = max(maxValue(VarSatck))+1
  Min = min(minValue(VarSatck))
  brks = seq(Min,Max,by=0.1)
  nbrks = length(brks)-1
  r.range = c(Min, Max)

  rasTot = raster(ncol=2, nrow=1)
values(rasTot) = c(Min,Max)
  
par(mfrow=c(1,3))

plot(VarSatck, breaks=brks,col=pal.2(nbrks), legend = F, zlim=c(Min,Max), 
main = "Frequency of all fire types")
plot(rasTot, legend.only=TRUE, col=pal.2(nbrks),
    legend.width=1, legend.shrink=0.75,
    legend.args=list(text="??",
                     side=4, font=2, line=2.5, cex=0.8))

VarSatck = RasterStack_AccF
  Max = max(maxValue(VarSatck))+1
  Min = min(minValue(VarSatck))
  brks = seq(Min,Max,by=0.1)
  nbrks = length(brks)-1
  r.range = c(Min, Max)

par(mfrow=c(1,3))

plot(VarSatck, breaks=brks,col=pal.2(nbrks), legend = F, zlim=c(Min,Max), 
main = "Frequency of accidental fire")
plot(rasTot, legend.only=TRUE, col=pal.2(nbrks),
    legend.width=1, legend.shrink=0.75,
    legend.args=list(text="??",
                     side=4, font=2, line=2.5, cex=0.8))

VarSatck = RasterStack_NatF
  Max = max(maxValue(VarSatck))+1
  Min = min(minValue(VarSatck))
  brks = seq(Min,Max,by=0.1)
  nbrks = length(brks)-1
  r.range = c(Min, Max)

par(mfrow=c(1,3))

plot(VarSatck, breaks=brks,col=pal.2(nbrks), legend = F, zlim=c(Min,Max), 
main = "Frequency of natural fire")
plot(rasTot, legend.only=TRUE, col=pal.2(nbrks),
    legend.width=1, legend.shrink=0.75,
    legend.args=list(text="??",
                     side=4, font=2, line=2.5, cex=0.8))

VarSatck = RasterStack_RxF
  Max = max(maxValue(VarSatck))+1
  Min = min(minValue(VarSatck))
  brks = seq(Min,Max,by=0.1)
  nbrks = length(brks)-1
  r.range = c(Min, Max)

par(mfrow=c(1,3))

plot(VarSatck, breaks=brks,col=pal.2(nbrks), legend = F, zlim=c(Min,Max), 
main = "Frequency of prescribed fire")
plot(rasTot, legend.only=TRUE, col=pal.2(nbrks),
    legend.width=1, legend.shrink=0.75,
    legend.args=list(text="??",
                     side=4, font=2, line=2.5, cex=0.8))

```


```{r FWI}

FWI_Tot = c("Year", "FWI", "FWI_Min","FWI_Max", "T_Min", "T_Max", "Ppt_Total","Scenario")

Event_Tot = c("Year", "Day", "FWI", "Scenario")

for(scenario in ListScenario){
    
    if(scenario == "BAU") {Input = BAU_input
    } else if(scenario == "Adapty"){Input = Adapty_input
    } else {Input = ProAct_input}
  
  Clim = paste(Input,"..1/Climate-future-input-log.csv",sep="") %>% read.csv()
  list_year = Clim$Year %>% unique()

  for(year in list_year) {
    FWI = Clim$FWI[Clim$Year == year] %>% mean()
    FWImin = Clim$FWI[Clim$Year == year] %>% min()
    FWImax = Clim$FWI[Clim$Year == year] %>% max()
    Tmin = Clim$min_airtemp[Clim$Year == year] %>% min()
    Tmax = Clim$max_airtemp[Clim$Year == year] %>% max()
    Psum = Clim$ppt[Clim$Year == year] %>% sum()
    
    FWI_Tot = rbind(FWI_Tot, c(year, FWI, FWImin, FWImax, Tmin, Tmax, Psum, scenario))
    
    Event = paste0(Input,"..1/scrapple-events-log.csv") %>% read.csv()
    
    EventFWI = cbind(Event$SimulationYear, Event$InitialDayOfYear, Event$MeanFWI) %>% as.data.frame()
    EventFWI$Scenario = scenario
    
    Event_Tot = rbind(Event_Tot, EventFWI)
  }
}

FWI_Tot = as.data.frame(FWI_Tot)
colnames(FWI_Tot)=FWI_Tot[1,] %>% unlist %>% as.character
FWI_Tot=FWI_Tot[-1,]

j=c(1:7)

FWI_Tot[ , j] = apply(FWI_Tot[ , j], 2,
                    function(x) as.numeric(as.character(x)))

Event_Tot = as.data.frame(Event_Tot)
colnames(Event_Tot)=Event_Tot[1,] %>% unlist %>% as.character
Event_Tot=Event_Tot[-1,]

j=c(1:3)

Event_Tot[ , j] = apply(Event_Tot[ , j], 2,
                    function(x) as.numeric(as.character(x)))

```

```{r pFWI}

FWIp = ggplot(FWI_Tot, aes(x=Year, y=FWI)) +
  geom_line() +
  xlab("year")+
  ylab("Mean fire weather index")

Maxp = ggplot(FWI_Tot, aes(x=Year, y=FWI_Max)) +
  geom_line(color="red") +
  xlab("year")+
  ylab("Max fire weather index")

Minp = ggplot(FWI_Tot, aes(x=Year, y=FWI_Min)) +
  geom_line(color="blue") +
  xlab("year")+
  ylab("Min fire weather index")

plot_grid(Maxp, FWIp, Minp, labels="AUTO", ncol = 1, nrow = 3)

```

```{r event}

ggplot(Event_Tot, aes(x=Scenario, y=FWI, col=Scenario)) +
  geom_boxplot() +
  stat_summary(fun=mean, geom="point", shape=4, size=3) +
  ylab("Fire Weather Index") +
  ggtitle("Mean Fire Weather Index for all the events") +
  theme(plot.title = element_text(hjust = 0.5))

Event_Ag = aggregate(data=Event_Tot, FWI~Year, mean)

ggplot(Event_Ag, aes(x=Year, y=FWI)) +
  geom_line() +
  xlab("year")+
  ylab("Mean fire weather index")+
  ggtitle("Mean Fire Weather Index for all the events") +
  theme(plot.title = element_text(hjust = 0.5))
  

```


```{r pVar}
Tminp = ggplot(FWI_Tot, aes(x=Year, y=T_Min)) +
  geom_line(color="blue") +
  xlab("year")+
  ylab("Min temperatures")

Tmaxp = ggplot(FWI_Tot, aes(x=Year, y=T_Max)) +
  geom_line(color="red") +
  xlab("year")+
  ylab("Max temperatures")

Pp = ggplot(FWI_Tot, aes(x=Year, y=Ppt_Total)) +
  geom_line() +
  xlab("year")+
  ylab("Total precipitations")

plot_grid(Tmaxp, Tminp, Pp, labels="AUTO", ncol = 1, nrow = 3)

```


# VI. Forest sustainability and biodiverity

## VI.a) Sustaiability of the forest

### VI.a.1) Repartition of the biomass

```{r BMTot}

StackCovDif = stack()
StackBM = stack()

for(i in c(1,2)){
  
  if(i == 1) {BAU_inputBM == BAU_inputBM1 &
    Adapty_inputBM == Adapty_inputBM1 &
    ProAct_inputBM == ProAct_inputBM1
  } else {BAU_inputBM == BAU_inputBM2 &
    Adapty_inputBM == Adapty_inputBM2 &
    ProAct_inputBM == ProAct_inputBM2}

for(scenario in ListScenario){
    
  if(scenario == "BAU") {Input = BAU_inputBM
  } else if(scenario == "Adapty"){Input = Adapty_inputBM
  } else {Input = ProAct_inputBM}

  FxR0 = paste0(Input,"FX_R_SEED-0.tif") %>% raster()
  FxR100 = paste0(Input,"FX_R_SEED-100.tif") %>% raster()

  NFxR0 = paste0(Input,"NOFX_R_SEED-0.tif") %>% raster()
  NFxR100 = paste0(Input,"NoFX_R_SEED-100.tif") %>% raster()

  NFxNR0 = paste0(Input,"NOFX_NOR_SEED-0.tif") %>% raster()
  NFxNR100 = paste0(Input,"NoFX_NOR_SEED-100.tif") %>% raster()

  Shrub0 = FxR0 + NFxR0 + NFxNR0
  Shrub100 = FxR100 + NFxR100 + NFxNR100

  BMTot0 = paste0(Input,"TotalBiomass-0.tif") %>% raster()
  BMTot100 = paste0(Input,"TotalBiomass-100.tif") %>% raster()
  
  BMTot0[BMTot0 >= 300000] = NA
  
  BMdiff = BMTot100-BMTot0
  
  BMTot0[BMTot0 == 0] = NA
  BMTot100[BMTot100 == 0] = NA
  BMdiff[BMdiff == 0] = NA
  
  Covert0 = 1-(Shrub0/BMTot0)
  Covert100 = 1-(Shrub100/BMTot100)

  CovDif = Covert100-Covert0
    
  names(CovDif) = paste0("CovDif_",scenario)
  StackCovDif = addLayer(StackCovDif, CovDif)
    
  names(BMTot0) = paste0("BMTot0_",scenario)
  names(BMTot100) = paste0("BMTot100_",scenario)
  names(BMdiff) = paste0("BMdiff_",scenario)
  StackBM = addLayer(StackBM, BMTot0,BMTot100,BMdiff)

}

Title = "Total Biomass"
Min = 0
Max = 170000
brks = seq(Min,Max,by=10000)
nbrks = length(brks)-1
r.range = c(Min, Max)

rasTot = raster(ncol=2, nrow=1)
values(rasTot) = c(Min,Max)

tmp = StackBM[[1]]
plot(tmp, breaks=brks,col=pal.2(nbrks), legend = F, zlim=c(Min,Max), 
main = "Initial situation")
plot(rasTot, legend.only=TRUE, col=pal.2(nbrks),
    legend.width=1, legend.shrink=0.75,
    legend.args=list(text=Title, side=4, font=2, line=2.5, cex=0.8))

par(mfrow=c(1,3))  
for(i in c(2,5,8)){
  tmp = StackBM[[i]]
  plot(tmp, breaks=brks,col=pal.2(nbrks), legend = F, zlim=c(Min,Max), 
  main = names(tmp))
  plot(rasTot, legend.only=TRUE, col=pal.2(nbrks),
      legend.width=1, legend.shrink=0.75,
      legend.args=list(text=Title, side=4, font=2, line=2.5, cex=0.8))
}

Title = "Total Biomass"
Min = -130000
Max = 130000
brks = c(-130000, -80000,-40000, 0, 40000, 80000,130000)
nbrks = length(brks)-1
r.range = c(Min, Max)

rasTot = raster(ncol=2, nrow=1)
values(rasTot) = c(Min,Max)

par(mfrow=c(1,3))
for(i in c(3,6,9)){
  tmp = StackBM[[i]]
  plot(tmp, breaks=brks,
       col=pal.dif(6), legend = T, zlim=c(Min,Max), 
  main = names(tmp))
  }

```


### VI.a.2) Patterns of regeneration

### VI.a.3) Evolution of the forest cover

```{r fc}

Title = "Forest cover evolution"
Min = min(minValue(StackCovDif))
Max = max(maxValue(StackCovDif))
brks = seq(Min,Max,by=0.001)
nbrks = length(brks)
r.range = c(Min, Max)

rasTot = raster(ncol=2, nrow=1)
values(rasTot) = c(Min,Max)

par(mfrow=c(1,3))  
for(i in c(1:3)){
  tmp = StackCovDif[[i]]
  plot(tmp, breaks=brks,col=pal.2(nbrks), legend = F, zlim=c(Min,Max), 
  main = names(tmp))
  plot(rasTot, legend.only=TRUE, col=pal.2(nbrks),
      legend.width=1, legend.shrink=0.75,
      legend.args=list(text=Title, side=4, font=2, line=2.5, cex=0.8))
}

```


## IV.b) Biodiverity on the forest

Don't take into account the 0.

```{r biodiv1}


Biodiv = c(c("Year", "Scenario", "Spp_Rich_mean", "Age_Richness_mean"))

Stack=stack()

for(year in seq(0, 100, by=10)){
  for(scenario in ListScenario){
    
    if(scenario == "BAU") {Input = BAU_input
    } else if(scenario == "Adapty"){Input = Adapty_input
    } else {Input = ProAct_input}
  
    SppRich = paste(Input,"..1/outputs/spp-counts/SPP-RICH-",
                       year,".img",sep="") %>% raster()
    SppRich[SppRich == 0] = NA
    SppRich_mean = cellStats(SppRich, stat='mean', na.rm=TRUE)
    
    if(year %in% c(0, 100)){
      Q = quantile(SppRich, probs = c(0.25, 0.75))
      SppRichQ = SppRich
      SppRichQ[SppRichQ <= Q[2] & SppRichQ > Q[1]] = NA
      SppRichQ[SppRichQ <= Q[1]] = 0
      SppRichQ[SppRichQ > Q[2]] = 1
  
      names(SppRich) = paste0("SppRich_",scenario,year)
      names(SppRichQ) = paste0("SppRichQ_",scenario,year)
      Stack = addLayer(Stack, SppRich, SppRichQ)
    }
    AgeRichness = paste(Input,"..1/outputs/age-all-spp/AGE-AVG-",
                       year,".img",sep="") %>% raster()
    AgeRichness[AgeRichness == 0] = NA
    AgeRichness_mean = cellStats(AgeRichness, stat='mean', na.rm=TRUE)
    
    if(year%in% c(0, 100)){
      Q = quantile(AgeRichness, probs = c(0.25, 0.75))
      AgeRichnessQ = AgeRichness
      AgeRichnessQ[AgeRichnessQ <= Q[2] & AgeRichnessQ > Q[1]] = NA
      AgeRichnessQ[AgeRichnessQ <= Q[1]] = 0
      AgeRichnessQ[AgeRichnessQ > Q[2]] = 1
    
      names(AgeRichness) = paste0("AgeRichness_",scenario,year)
      names(AgeRichnessQ) = paste0("AgeRichnessQ_",scenario,year)
      Stack = addLayer(Stack, AgeRichness, AgeRichnessQ)
    }
    
    Biodiv = rbind(Biodiv, c(year, scenario, SppRich_mean, AgeRichness_mean))
    }
  }
  
colnames(Biodiv)=Biodiv[1,] %>% unlist %>% as.character
Biodiv=Biodiv[-1,] %>% as.data.frame()

j=c(1,3,4)

Biodiv[ , j] = apply(Biodiv[ , j], 2,
                    function(x) as.numeric(as.character(x)))

```


```{r plotstack, fig.width = 20}

# par(mar=c(4.1,4.1,12.4,10.5))

for(i in c(1,3)){
  VarSatck = stack(Stack[[i]],Stack[[i+12]],
                   Stack[[i+16]],Stack[[i+20]])
  Max = max(maxValue(VarSatck))+1
  Min = min(minValue(VarSatck))
  brks = seq(Min,Max,by=0.1)
  nbrks = length(brks)-1
  r.range = c(Min, Max)

  rasTot = sum(VarSatck)
  
  par(mfrow=c(1,2))
  for(i in seq_len(nlayers(VarSatck))){
    tmp = VarSatck[[i]]
    plot(tmp, breaks=brks,col=pal.2(nbrks), legend = F, zlim=c(Min,Max), 
    main = names(tmp))
    plot(rasTot, legend.only=TRUE, col=pal.2(nbrks),
       legend.width=1, legend.shrink=0.75)
  }}

```

```{r plotstack2,}
for(i in c(2,4)){
  VarSatck = stack(Stack[[i]],Stack[[i+12]],
                   Stack[[i+16]],Stack[[i+20]])
  Max = 1
  Min = 0
  brks = c(0, 0.5, 1)
  nbrks = 2
  r.range = c(Min, Max)

  rasTot = raster(ncol=2, nrow=1)
  values(rasTot) = c(Min,Max)
  
  par(mfrow=c(1,2))
  for(i in seq_len(nlayers(VarSatck))){
    tmp = VarSatck[[i]]
    plot(tmp, breaks=brks,col=pal.2(nbrks), legend = F, zlim=c(Min,Max), 
    main = names(tmp))
    plot(rasTot, legend.only=TRUE, col=pal.2(nbrks),
       legend.width=1, legend.shrink=0.75)
}}
```


```{r divplot}

pSR = ggplot(Biodiv, aes(x=Year, y=Spp_Rich_mean, col=Scenario, shape = Scenario)) +
  geom_point() +
  scale_x_continuous(name= "Time (in years)") +
  scale_y_continuous(name = "Species richness")+#, limits =c(2.126, 2.127))
  ggtitle("Evolution of the species richness") +
  theme(plot.title = element_text(hjust = 0.5))
  
pAR = ggplot(Biodiv, aes(x=Year, y=Age_Richness_mean, col=Scenario, shape = Scenario)) +
  geom_point() +
  scale_x_continuous(name= "Time (in years)") +
  scale_y_continuous(name = "Age richness")+#, limits =c(2.126, 2.127))
  ggtitle("Evolution of the age richness") +
  theme(plot.title = element_text(hjust = 0.5))

  
  plot_grid(pSR, pAR, labels="AUTO", ncol = 2, nrow = 1)

```


