---
title: "Stands and Managment Areas maps"
author: "Vincent BISQUAY GRACIA"
date: "07/2021"
output:
  pdf_document: default
  html_document: default
---



# I. Set up

Used pakages :

```{r setup, message=FALSE, warning=FALSE}
wd = "D:/Internship 3A/GitHub/Project-Klamath-2021/Model Parameterization"
setwd(wd)
library(sf)
library(raster)
library(rgdal)
library(devtools)
library(magrittr)
library(nngeo)
library(knitr)

```


3 rasters are imported :

The raster layer of the ecoregions *ER_OnlyCA*, has the extent of the study zone (The Californian part of the Klamath mountains).

The two raster layers of the managment areas *Ownership_TotKlamath* and of the stands *Stands_TotKlamath* have an extent superior to the study zone (the Oregon part of the Klamath mountain is also contained).

```{r import}

ER_OnlyCA = 
  paste0(wd,"/Study_site/ecoregions_v2.tif") %>% raster()

Ownership_TotKlamath = 
  paste0(wd,"/Study_site/E4_ownership_BAU_v4.tif") %>% raster()

Stands_TotKlamath = 
  paste0(wd,"/Study_site/E4_stands_BAU_v5.tif") %>% raster()


```

We want that the management area and stands rasters have the same extent and defintion than the ecoregion one. This will allow all rasters to have the same definition and allow LANDIS-II to compute the landscape properly.

# II. Selection of the Ownership and Stand areas included in the study area

## II.a) A shapefile with all the borders of the study area is created

Polygons are created with the Ecoregions raster. Then, all the polygons are merged in an unique polygon *Study site* that have the extent of the study area.

```{r poly}

ER_OnlyCA[ER_OnlyCA == 0] <- NA # We don't want the background
ER_OnlyCA_poly = rasterToPolygons(ER_OnlyCA, fun=function(x){x > 0}, dissolve = T)

Study_site = ER_OnlyCA_poly %>% st_as_sf %>%
  st_union %>% st_remove_holes %>% st_as_sf

par(mfrow = c(1,2))
plot(Study_site, main = "Figure 1: Borders of the study area")
plot(ER_OnlyCA, main = "Figure 2: Reference Layer")


```


## II.b) All cells out of the study area are set to NA

In this fist step, all the cells of the stand raster and the management area raster that are not in the Study Area are set to NA.

```{r filter}
Ownership_OnlyCA_select = mask(Ownership_TotKlamath, Study_site)
Stands_OnlyCA_select = mask(Stands_TotKlamath, Study_site)

par(mfrow=c(2,2))
plot(Ownership_TotKlamath, main = "Figure 3.a: Ownership layer", xaxt="n", yaxt="n")
plot(Ownership_OnlyCA_select, main = "Figure 3.b: Ownership in study area", xaxt="n",
     yaxt="n")
plot(Stands_TotKlamath, main = "Figure 3.c: Stands layer", xaxt="n", yaxt="n")
plot(Stands_OnlyCA_select, main = "Figure 3.d: Stands in study area", xaxt="n", yaxt="n")

```



After this operation, the two layers we are modifying present a large number of empty cells that does not exist on the reference layer. Thus, other transformations are needed.

## II.c) The rasters are croped to the study area extent

```{r crop}

Ownership_OnlyCA_Crop = crop(Ownership_OnlyCA_select,ER_OnlyCA)
Stands_OnlyCA_Crop = crop(Stands_OnlyCA_select,ER_OnlyCA)

par(mfrow=c(2,2))
plot(Ownership_OnlyCA_select, main = "Figure 4.a: Ownership in study area", xaxt="n",
     yaxt="n")
plot(Ownership_OnlyCA_Crop, main = "Figure 4.b: Ownership croped", xaxt="n", yaxt="n")
plot(Stands_OnlyCA_select, main = "Figure 4.c: Stands in study area", xaxt="n", yaxt="n")
plot(Stands_OnlyCA_Crop, main = "Figure 4.d: Stands croped", xaxt="n", yaxt="n")

```

The plots seems identical to the ecoregion one at this sage.

```{r rc2}
a = c(ER_OnlyCA@ncols, ER_OnlyCA@nrows)
b = c(Ownership_OnlyCA_Crop@ncols, Ownership_OnlyCA_Crop@nrows)
c = c(Stands_OnlyCA_Crop@ncols, Stands_OnlyCA_Crop@nrows)

df = rbind(a,b,c) %>% as.data.frame(row.names = c("Ecoregion", "Management area", "Stands"))
colnames(df) = c("X","Y")

kable(df, caption = "Number of cells by layer after croping")

```

However, the number of rows and columns of the obtained layers (`r toString(Stands_OnlyCA_Crop@ncols)`, `r toString(Stands_OnlyCA_Crop@nrows)`) is different than the targeted one (`r toString(ER_OnlyCA@ncols)`, `r toString(ER_OnlyCA@nrows)`)


## II.d) A resampling is done to have the same resolution

```{r resample}
Ownership_OnlyCA = resample(Ownership_OnlyCA_Crop, ER_OnlyCA, method="ngb")
Stands_OnlyCA = resample(Stands_OnlyCA_Crop, ER_OnlyCA, method="ngb")

par(mfrow=c(2,2))
plot(Ownership_OnlyCA_Crop, main = "Figure 5.a: Ownership croped", xaxt="n", yaxt="n")
plot(Ownership_OnlyCA, main = "Figure 5.b: Ownership resampled", xaxt="n", yaxt="n")
plot(Stands_OnlyCA_Crop, main = "Figure 5.c: Stands croped", xaxt="n", yaxt="n")
plot(Stands_OnlyCA, main = "Figure 5.d: Stands resampled", xaxt="n", yaxt="n")

```


```{r rc3}
a = c(ER_OnlyCA@ncols, ER_OnlyCA@nrows)
b = c(Ownership_OnlyCA@ncols, Ownership_OnlyCA@nrows)
c = c(Stands_OnlyCA@ncols, Stands_OnlyCA@nrows)

df = rbind(a,b,c) %>% as.data.frame(row.names = c("Ecoregion", "Management area", "Stands"))
colnames(df) = c("X","Y")

kable(df, caption = "Number of cells by layer after resampling")
```


This time the resolution is the same. Thus, the layers can be stacked and used in LANDIS-II.


# II.e) The obtained layers are exported

The *datatype* parameter is important, LANDIS-II works only with integers for these two layers. For a raster as heavy as *Stands_OnlyCA*, the data type "INT4S" is the only possibility.

```{r exp}
Ownership_OnlyCA[is.na(Ownership_OnlyCA[])] = 0
Stands_OnlyCA[is.na(Stands_OnlyCA[])] = 0

writeRaster(Ownership_OnlyCA,
            filename  = paste0(wd,"/Study_site/Ownership_OnlyCA.tif"),
            format = "GTiff", datatype ="INT1U",overwrite=T)

writeRaster(Stands_OnlyCA,
            filename  = paste0(wd,"/Study_site/Stands_OnlyCA.tif"),
            format = "GTiff", datatype ="INT4S",overwrite=T)

```



# III. Creation of the Resistence Management Areas

The Pro-active management scenario have a resistence prescription. This consists on identifying climate refugias and apply a productive management with species traditionaly used on such places.

As these refugias concentrate an important part of the economical insights, a buffer zone is created with intensive fire and insects prescriptions.

Some of the rasters used in this part have not a defined system of projection. The one of the management area is used as a reference.

```{r ref}

CRSRef = crs(Ownership_OnlyCA)
NrowRef = Ownership_OnlyCA@nrows
NcolRef = Ownership_OnlyCA@ncols
ResRef = res(Ownership_OnlyCA)[1]
XminRef = Ownership_OnlyCA@extent@xmin
XmaxRef = Ownership_OnlyCA@extent@xmax
YminRef = Ownership_OnlyCA@extent@ymin
YmaxRef = Ownership_OnlyCA@extent@ymax

```


## III.a) Identification of the climate refugias

The first step is to identify the climate change refugias, i.e. zones where the effect of the climate change on the ecosystem (and particularly tree health) is limited comared to the wole landscape.

The proxy used to identify these zones are the soil moisture. This choice is justified and discussed in the report. Among the input files used in LANDIS-II, there is no raster of the soil moisture. The layer used here is the soil moisture modelled on year 1 by the NECN extention, in the scenario Business As Usual.

```{r sm}
SoilMoist = paste0(wd, "/Study_site/Annual-water-budget-1.img") %>% raster()

plot(SoilMoist, main = "Figure 6: Soil moisture in the study site")

```

The quatile 0.95, i.e. the 5% of the cells with the highest value of soil moisture, is selected (the cells take the value 11, while the others are eraised).

```{r sm1}

Q = quantile(SoilMoist, probs = c(0.05, 0.95))

Q3 = as.numeric(Q[2])

values(SoilMoist)[values(SoilMoist) < Q3] = NA

values(SoilMoist)[values(SoilMoist) > 0] = 11

```

A raster is created with this quantile using the data of the reference raster.

```{r smr}

SoilMoist = raster(vals=getValues(SoilMoist),
                    nrow=NrowRef,ncol=NcolRef,resolution=ResRef,
                    xmn=XminRef, xmx=XmaxRef,ymn =YminRef,ymx=YmaxRef,crs=CRSRef)

plot(SoilMoist, main = "Figure 7: Zones with high soil moisture")

freq(SoilMoist, merge=T) %>% as.data.frame() %>% kable(caption = "Number of cells in the potential refugias raster by value")

```


This zone of high soil moisture is considered as the potentials climate refugias and will be used for the resistence prescription.

## III.b) Creation of the buffer zone

A buffer of 300 m, corresponding to a width of 2 cells, is created. Similarly to before, all cells in it are set to 12 and the others eraised.

```{r buf}
Buf = buffer(SoilMoist, width=300)

values(Buf)[values(Buf) == 1] = 12

Buf = raster(vals=getValues(Buf),
                    nrow=NrowRef,ncol=NcolRef,resolution=ResRef,
                    xmn=XminRef, xmx=XmaxRef,ymn =YminRef,ymx=YmaxRef,crs=CRSRef)

plot(Buf, main = "Figure 8: Buffer zone around the resistence management area")

freq(Buf, merge=T) %>% as.data.frame() %>% kable(caption = "Number of cells in the buffer raster by value")

```

## III.c) Creation of the buffer zone

The potential climate refugia raster and the buffer zone raster are both merge

```{r merge}

Resistence = cover(SoilMoist, Buf)

plot(Resistence)

New_Ma = cover(Resistence, Ownership_OnlyCA)

plot(New_Ma)

freq(New_Ma, merge=T) %>% as.data.frame() %>% tail()

```

```{r stand}

SoilMoist[is.na(SoilMoist)] = 0

Buf[is.na(Buf)] = 0

StandRefugia = Stands_OnlyCA + SoilMoist + Buf

plot(StandRefugia)

writeRaster(StandRefugia,
filename =  paste0(wd,"/Study_site/Stand_CA_Refugias.tif"),
format = "GTiff", datatype ="INT4S",overwrite=T)

```


```{r verif}


names(New_Ma) = "New_Ma"
names(StandRefugia) = "StandRefugia"

### Stacking lets us see where they overlap
Stack = stack(New_Ma,StandRefugia)

### This will show where all the duplicates exist. 
Stack_df = as.data.frame(Stack)
Val = unique(Stack_df[ , 1:2 ])

Ndup = sum(duplicated(Val[,2]))

Dupl = subset(Val, duplicated(Val[,2]))

for(i in c(1:Ndup)){
  DupStand = Dupl[i,2]
  DupMA = Stack$New_Ma[Stack$StandRefugia==DupStand] %>% unique()
  
  if(DupMA[1] %in% c(11,12)) {
    Select_Ma = DupMA[1]
    No_Ma = DupMA[2]
    
  }else{
    Select_Ma = DupMA[2]
    No_Ma = DupMA[1]}
  
  Stack$New_Ma[Stack$StandRefugia==DupStand &Stack$New_Ma==No_Ma] = Select_Ma
}


### And write the new management file
### This can be done in reverse, to change stands to a given managment. 

MA_Refugia = Stack$New_Ma

writeRaster(MA_Refugia,
filename =  paste0(wd,"/Study_site/Ownership_CA_Refugias.tif"),
format = "GTiff", datatype ="INT1U",overwrite=T)
```

# VI. Plot of the Management areas

```{r MA}

pal.11 = colorRampPalette(c("white", "grey", "purple","grey","tomato","green4","green","yellow","red","grey","grey"))

pal.13 = colorRampPalette(c("white", "grey", "purple","grey","tomato","green4","green","yellow","red","grey","grey", "cyan","blue"))

pal.R = colorRampPalette(c("white", "grey", "grey","grey","grey","grey","grey","grey","grey","grey","grey", "cyan","blue"))

par(mfrow=c(2,2))
plot(Ownership_OnlyCA, main="Managment areas (BAU and Adaptability)",
     col=pal.11(11))
plot(MA_Refugia, main="Managment areas (Pro-Active)",
     col=pal.13(13))
plot(MA_Refugia, main="Resistence areas",
     col=pal.R(13))

data.frame("Management area" =c("Unmanaged","Federal","Unmanaged","Tribal Area","PIF", "PNIF",
                                "Matrix timberlands", "AMA","Unmanaged","Unmanaged")) %>%
  kable(caption = "Management areas map code")

```



