---
title: "Comparison of two climatic models"
author: "Vincent BG"
date: "06/08/2021"
output:
  pdf_document: default
  html_document: default
---

The aim of this document is to determine why fires are decreasing in intensity, a result in contradiction with the bibliography.

# I) Set up

```{r setup, message=FALSE, warning=FALSE}

wd = "D:/Internship 3A/GitHub/Project-Klamath-2021/Outputs/R"
setwd(wd)
library(raster)
library(rgdal)
library(devtools)
library(sf)
library(nngeo)
library(ggplot2)
library(ggrepel)
library(cowplot)
library(spatialEco)
library(magrittr)
library(svMisc)

```



```{r setup}

wd = "D:/Internship 3A/GitHub/Project-Klamath-2021/Outputs/R"
setwd(wd)

```

```{r data}

BAU_input =
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest BAU/"
Adapty_input = 
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest Adaptability/"
ProAct_input =
  "E:/FIF/Stage 3A/Extract/Documents/Klamath_(CA_only)_2021 - Harvest Pro-active/"

ListScenario = c("Business As usual","Adaptability","Pro-Active")

```

# II) Results obtained with the model Miroc

This model is the one used on all the study. It is used by LANDIS-II to generate a set of climatic data that is used during the simulation.

From this data, the Fire Weather Index (FWI), an important climatic factor of the model for fire simulation, is stored with some of his components to be analysed.

```{r FWITot}

FWI_Tot = c("Year", "FWI", "FWI_Min","FWI_Max", "T_Min", "T_Max", "Ppt_Total")

Clim = paste0(BAU_input, "..1/Climate-future-input-log.csv") %>% read.csv()
list_year = Clim$Year %>% unique()

for(year in list_year) {
  FWI = Clim$FWI[Clim$Year == year] %>% mean()
  FWImin = Clim$FWI[Clim$Year == year] %>% min()
  FWImax = Clim$FWI[Clim$Year == year] %>% max()
  Tmin = Clim$min_airtemp[Clim$Year == year] %>% min()
  Tmax = Clim$max_airtemp[Clim$Year == year] %>% max()
  Psum = Clim$ppt[Clim$Year == year] %>% sum()
  FWI_Tot = rbind(FWI_Tot, c(year, FWI, FWImin, FWImax, Tmin, Tmax, Psum))
}

FWI_Tot = as.data.frame(FWI_Tot)
colnames(FWI_Tot)=FWI_Tot[1,] %>% unlist %>% as.character
FWI_Tot=FWI_Tot[-1,]

j=c(1:7)

FWI_Tot[ , j] = apply(FWI_Tot[ , j], 2,
                    function(x) as.numeric(as.character(x)))

```

The FWI of the days where fire happends is also stocked. 

```{r FWI}

Event_Tot = c("Year", "Day", "FWI", "Scenario", "Run")

for(j in c(1,2)){
  if(j == 1) { run = "..1"
  } else { run = "..2"}
  
  for(scenario in ListScenario){
    if(scenario == "Business As usual") {Input = BAU_input
    } else if(scenario == "Adaptability"){Input = Adapty_input
    } else {Input = ProAct_input}
    
    Event = paste0(Input, run, "/scrapple-events-log.csv") %>% read.csv()
    
    EventFWI = cbind(Event$SimulationYear, Event$InitialDayOfYear, Event$MeanFWI) %>% as.data.frame()
    EventFWI$Scenario = scenario
    EventFWI$Run = run
    
    Event_Tot = rbind(Event_Tot, EventFWI)
  }
}

Event_Tot = as.data.frame(Event_Tot)
colnames(Event_Tot)=Event_Tot[1,] %>% unlist %>% as.character
Event_Tot=Event_Tot[-1,]

j=c(1:3)

Event_Tot[ , j] = apply(Event_Tot[ , j], 2,
                    function(x) as.numeric(as.character(x)))

```


```{r pFWI}

FWIp = ggplot(FWI_Tot, aes(x=Year, y=FWI)) +
  geom_line() +
  xlab("year")+
  ylab("Mean fire weather index")

Maxp = ggplot(FWI_Tot, aes(x=Year, y=FWI_Max)) +
  geom_line(color="red") +
  xlab("year")+
  ylab("Max fire weather index")

Minp = ggplot(FWI_Tot, aes(x=Year, y=FWI_Min)) +
  geom_line(color="blue") +
  xlab("year")+
  ylab("Min fire weather index")

plot_grid(Maxp, FWIp, Minp, labels="AUTO", ncol = 1, nrow = 3)

```

```{r pVar}
Tminp = ggplot(FWI_Tot, aes(x=Year, y=T_Min)) +
  geom_line(color="blue") +
  xlab("year")+
  ylab("Min temperatures")

Tmaxp = ggplot(FWI_Tot, aes(x=Year, y=T_Max)) +
  geom_line(color="red") +
  xlab("year")+
  ylab("Max temperatures")

Pp = ggplot(FWI_Tot, aes(x=Year, y=Ppt_Total)) +
  geom_line() +
  xlab("year")+
  ylab("Total precipitations")

plot_grid(Tmaxp, Tminp, Pp, labels="AUTO", ncol = 1, nrow = 3)

```

```{r event}

ggplot(Event_Tot, aes(x=Scenario, y=FWI, col=Scenario)) +
  geom_boxplot() +
  stat_summary(fun=mean, geom="point", shape=4, size=3) +
  ylab("Fire Weather Index") +
  ggtitle("Mean Fire Weather Index for all the events") +
  theme(plot.title = element_text(hjust = 0.5))

Event_Ag = aggregate(data=Event_Tot, FWI~Year, mean)

ggplot(Event_Ag, aes(x=Year, y=FWI)) +
  geom_line() +
  xlab("year")+
  ylab("Mean fire weather index")+
  ggtitle("Mean Fire Weather Index for all the events") +
  theme(plot.title = element_text(hjust = 0.5))
  

```


```{r a}
Event_Tot = c("Year", "Day", "FWI", "Scenario")

  
Event = paste0(BAU_input,"..1/scrapple-events-log.csv") %>% read.csv()
    
EventFWI = cbind(Event$SimulationYear, Event$InitialDayOfYear, Event$MeanFWI) %>% as.data.frame()
EventFWI$Scenario = scenario
    
Event_Tot = rbind(Event_Tot, EventFWI)



Event_Tot = as.data.frame(Event_Tot)
colnames(Event_Tot)=Event_Tot[1,] %>% unlist %>% as.character
Event_Tot=Event_Tot[-1,]

j=c(1:3)

Event_Tot[ , j] = apply(Event_Tot[ , j], 2,
                        function(x) as.numeric(as.character(x)))

Event_Ag = aggregate(data=Event_Tot, FWI~Year, mean)

ggplot(Event_Ag, aes(x=Year, y=FWI)) +
  geom_line() +
  xlab("year")+
  ylab("Mean fire weather index")+
  ggtitle("Mean Fire Weather Index for all the events") +
  theme(plot.title = element_text(hjust = 0.5))

```

cansm

```{r b}
Event_Tot2 = c("Year", "Day", "FWI", "Scenario")

Event2 = paste0(BAU_input,"..Clim2/scrapple-events-log.csv") %>% read.csv()
  
EventFWI2 = cbind(Event2$SimulationYear, Event2$InitialDayOfYear, Event2$MeanFWI) %>% as.data.frame()
EventFWI2$Scenario = scenario
  
Event_Tot2 = rbind(Event_Tot2, EventFWI2)


Event_Tot2 = as.data.frame(Event_Tot2)
colnames(Event_Tot2)=Event_Tot2[1,] %>% unlist %>% as.character
Event_Tot2=Event_Tot2[-1,]

j=c(1:3)

Event_Tot2[ , j] = apply(Event_Tot2[ , j], 2,
                        function(x) as.numeric(as.character(x)))

Event_Ag2 = aggregate(data=Event_Tot2, FWI~Year, mean)

ggplot(Event_Ag2, aes(x=Year, y=FWI)) +
  geom_line() +
  xlab("year")+
  ylab("Mean fire weather index")+
  ggtitle("Mean Fire Weather Index for all the events") +
  theme(plot.title = element_text(hjust = 0.5))

```

